---
title: "Resume"
description: "Professional resume highlighting expertise in Market Operation Analysis at Bank of America."
---

```{r}
library(vitae)
# Example CV content
bibliography_entries("cv-entries.bib") %>%
  detailed_entries(
    what = title,
    when = year,
    with = institution,
    where = location
  )
```

# Resume

Welcome to my professional resume, showcasing my experience and skills in **Market Operation Analysis** at **Bank of America**. Below is a detailed overview of my education, work experience, skills, and achievements.

## Contact Information
- **Name**: [Bryant Hq]  
- **Email**: bryantha@cpp.edu  
- **Phone**: (123) 456-7890  
- **Location**: [LA, CA]

## Professional Summary
Results-driven Market Operation Analyst with over 3 years of experience in data-driven marketing, digital strategy, and operational efficiency at Bank of America. Skilled in R programming, data visualization, and campaign optimization, with a proven track record of increasing customer engagement and profitability.

---

## Education

```{r}
# Load vitae package
library(vitae)

# Inline education data
education_data <- data.frame(
  degree = c("B.S. in Human Resources Leadership"),
  institution = c("CAl Poly Pomona"),
  location = c("Pomona, CA"),
  year = c(2021)
)
# Render education section
education_data %>%
  detailed_entries(
    what = degree,
    when = year,
    with = institution,
    where = location
  )
```


```{r}
# Inline work experience data
work_experience <- data.frame(
  title = c("Market Operation Analyst", "Marketing Intern"),
  employer = c("Bank of America", "TechCorp Solutions"),
  location = c("Los Angeles, CA", "Remote"),
  start = c("2023-06", "2022-01"),
  end = c("Present", "2022-12"),
  details = c(
    "Led data-driven marketing campaigns, increasing engagement by 20% through customer segmentation.",
    "Assisted in digital marketing projects, optimizing ad spend by 15% using A/B testing."
  )
)

# Render work experience section
work_experience %>%
  detailed_entries(
    what = title,
    when = glue::glue("{start} -- {end}"),
    with = employer,
    where = location,
    why = details
  )
```



